Planning to Save Energy: How Information Format Affects Accuracy

### 2025-04-01 manuscript/manuscript.qmd
resync

See @tbl-s2-agg for a breakdown of the descriptive statistics. The ordinal regression analysis revealed that the USD reference class significantly increased the odds of higher error categories compared to the kWh reference class (OR = 9.68, 95% CI: [1.69, 53.4]). Participants in the USD condition were therefore substantially more likely to deviate from the target energy reduction goal compared to those in the kWh condition. In contrast, the Percentage condition’s odds ratio relative to kWh was more uncertain (OR = 2.78, 95% CI: [0.53, 15.0]), indicating that although there may be a trend toward reduced accuracy in the Percentage condition, the evidence was not definitive (@tbl-s2-ord).

>>>>

See @tbl-s2-agg for a breakdown of the descriptive statistics. The ordinal regression analysis (see @tbl-s2-reg) revealed that the USD reference class significantly increased the odds of higher error categories compared to the kWh reference class (OR = 9.68, 95% CI: [1.69, 53.4]). Participants in the USD condition were therefore substantially more likely to deviate from the target energy reduction goal compared to those in the kWh condition. In contrast, the Percentage condition’s odds ratio relative to kWh was more uncertain (OR = 2.78, 95% CI: [0.53, 15.0]), indicating that although there may be a trend toward reduced accuracy in the Percentage condition, the evidence was not definitive (@tbl-s2-ord).
